New catch functions from CATCH.nc file

### 2023-06-09 NewCatchWorkflow.Rmd
matches, so far so good

@@

>>>>

Time in this output is *timestep* not days.

@@

Read in saved files created previously in ms-keyrun and the one just created with the new functions. This is now comparing the "sampled" fishery data.

```{r}

mskeyrundir <- "/Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38"

scenario.name <- "nordic_runresults_01"

fisherycomp <- atlantisom::read_savedfisheries(mskeyrundir, "Catch")

from_nc <- fisherycomp$allfleet[[1]]

from_txt <- fisherycomp$census[[1]]

fgs <- atlantisom::load_fgs(mskeyrundir, "nordic_groups_v04.csv")

  aggcatchtons <- from_nc %>%
    dplyr::select(species, time, atoutput) %>%
    dplyr::mutate(year = ceiling(time / stepperyr)) %>%
    dplyr::group_by(species, year) %>%
    dplyr::summarise(yeartot = sum(atoutput))

  txtCatchtons <- from_txt %>%
    dplyr::select(species, time, atoutput) %>%
    dplyr::mutate(year = time / 365) %>%
    dplyr::left_join(dplyr::select(fgs, Code, Name), by = c("species" = "Name"))

  comparetons <- txtCatchtons %>%
    dplyr::left_join(aggcatchtons, by = c("Code" = "species", "year" = "year")) %>%
    ggplot2::ggplot() +
    geom_line(aes(year, atoutput)) +
    geom_point(aes(year, yeartot), color = "blue", alpha = 0.2) +
    facet_wrap( ~ species, scales = "free_y")
